---
title: 'Exercise 10: Data Manipulation with Replication Example'
author: "Marcy Shieh"
date: "11/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Extend the dataset

```{r}
#install/load packages 
library("magrittr")
library("tidyverse")
library("haven")
library("here")
library("stargazer")
library("modelsummary")
library(sjlabelled)
```

```{r}
here()
#bork data
bork <- read_dta("Bork.dta")
view(bork)

#congress data
congress111 <- read_dta("sen111kh.dta")
view(congress111)

#poole
poole <- read_dta("Weekly_DW-NOMINATE_31_9.DTA")
view(poole)

#trim whitespace 
poole$name <- trimws(poole$name)

# rename congress so they conform for merging
poole <- rename(poole, congress = cong)

view(poole)

#extend to sotomayor

#V262 is the sotomayor column, select this column and remove president
congress111_soto <- congress111 %>%
  select(cong:name, V262) %>%
  filter(name != "OBAMA")

# look at the breakdown
table(congress111_soto$V262)
#recode 6 to 0 and 0 to NA 
congress111_soto <- congress111_soto %>%
  mutate(
    vote = ifelse(V262 == 6,
                  0,
          ifelse(V262 == 0,
                 NA,
                 V262)
  ))

table(congress111_soto$V262)

#check names for merging
names(congress111_soto)
names(bork)
#Need to change congress111_soto to conform with bork
congress111_soto <- rename(congress111_soto, congress = cong)
#check to make sure 
view(congress111_soto)
#select pertinent variable 
sotomayor <- congress111_soto %>%
  select(congress, id, state, name, vote)

view(sotomayor)

#select the pertinent variables in poole
poole_select <- poole %>%
  select(congress, idno, statenm, name, dwnom1, party)

# merge sotomayor votes with the senators' common space scores
soto_poole <- left_join(sotomayor, poole_select, by=c("id" = "idno", "congress", "name"))
#check names
names(soto_poole)
#rename 
soto_poole <- rename(soto_poole, dwnom1 = cs1)

#make a dataframe with: nominee, presprty, sameprty, strngprs, nomid, 
#regime_dummy, lackqual, csnom, eucldist, interaction
soto_poole$nominee <- rep("SOTOMAYOR") # name of nominee
alito_poole$presprty <- rep(1) # president held party majority in Senate

#if senator is in the same party as the president, 100 for Dems 
soto_poole %>%
  mutate(sameprty = ifelse(party == 100,
                           1,
                           0))

soto_poole$nomid <- rep(0.780) # ideology score of the judicial nominee: https://en.wikipedia.org/wiki/Segal%E2%80%93Cover_score
soto_poole$regime_dummy <- rep(1) 
#pre- or post-bork (1 is post-bork, 0 is pre-bork)
soto_poole$lackqual <- rep(1-0.810) 
#subtract newspaper score by 1 to get their "lack of qualifications" score #https://en.wikipedia.org/wiki/Segal%E2%80%93Cover_score

#save for later 
soto_poole$csnom <- NA 
#this is going to be the Segal-Cover score for each nominee "transformed" as the Common Space/Poole & Rosenthal/DW-Nominate (it goes by many names) score

soto_poole$eucldist <- NA 
#Euclidean distance between the senator and the nominee

soto_poole$interaction <- NA 
#interaction of ideological distance and qualifications

soto_bork_poole <- full_join(bork, soto_poole)
names(soto_bork_poole)


#from reading the article, you know that you need the common space scores for each president as well
# the president is coded with a congressional district (cd) number of 0, and a state number (state) of 99
poole_filter <- poole %>%
  filter(cd == 0 & state == 99) %>%
  select(congress, name, dwnom1)

#rename name
poole_filter <- rename(poole_filter, pres = name)

#rename dwnom1
poole_filter <- rename(poole_filter, cspres = dwnom1)

#join together the cspres scores
soto_bork_poole_full <- full_join(soto_bork_poole, poole_filter)


soto_poole_coefficients <- lm(cspres ~ nomid, data = soto_bork_poole_full)
soto_poole_coefficients$coefficients

#scale the common space scores for alito
soto_bork_poole_full$csnom_soto <- 0.5669997 - 0.9788148 *soto_bork_poole_full$nomid

#calculate for ideological distance
soto_bork_poole_full$eucldist_soto <- (soto_bork_poole_full$csnom_soto - soto_bork_poole_full$cs1)^2

#calculate the interaction between ideological distance and qualifications
soto_bork_poole_full$interaction_soto <- soto_bork_poole_full$eucldist_soto*soto_poole$lackqual

view(soto_bork_poole_full)

```
Extend the exercise we did in class up to the Senate confirmation of Associate Justice Sonia Sotomayor, following the instructions in the `lecture-10.R` file.

Links to the datasets required to complete this exercise:

- Harvard Dataverse entry for the Epstein et al. (2006) article (includes PDF of article for reference): https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/W5CV8E&version=1.0

- Poole & Rosenthal scores from 2016: https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/W5CV8E&version=1.0

- 111th Congress roll call votes and dictionary: https://legacy.voteview.com/senate111.htm

- Segal-Cover scores: https://en.wikipedia.org/wiki/Segal%E2%80%93Cover_score

# Replication

Find replication materials for a paper and replicate a table within the paper.

    - There are many political science papers with data stored in the Stata (`.dta`) file  format accompanied by a Stata file (`.do`) file. In those cases, you will need to read the Stata file into R using the `haven` package and recreate your table of choice using R code. In other words, please do not turn in Stata code!
    
    - If you do find replication materials in R and would like to run the entire R script, please feel free to do so! Reviewing other people's replication materials is the best way to learn how scholars assemble their results.

Here are some great resources for finding articles with reproducible data.

- Political Science Replication (https://politicalsciencereplication.wordpress.com/)

- Harvard Dataverse (https://dataverse.harvard.edu/dataverse/harvard?q=&fq0=subject_ss%3A%22Social%20Sciences%22&types=dataverses%3Adatasets&sort=dateSort&order=desc)

- Recent articles from *Political Science Research and Methods*, *American Journal of Political Science*, *American Political Science Review*, and *Political Analysis*

    - You can access articles in the top journals by signing into the UW-Madison Library website (https://library.wisc.edu) with your UW netID



# Submit

Email me (mshieh2@wisc.edu) the link to your `ps811-exercises` repository when you are done.